\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-08-02 papers/methods/paper.tex
Adding to the table

At the most fundamental level, a supernova cosmology analysis is simply a mapping from an underlying population onto an observed population, where cosmology is encoded directly in the mapping function. The difficulty arises both in adequately describing the biases in the mapping function, and in adding sufficient, physically motivated flexibility in both of these populations whilst not adding \textit{too} much flexibility, such that model fitting becomes pathological due to increasing parameter degeneracies within the model. In the following sections, we will describe these layers, mapping functions, and occurrences of these fatal pathologies.

@@

@@

\begin{table}
	\centering
	\caption{{\green Top-level parameters defined in our model and a summary of their use. The parameters are broken into two sections, the top for parameters which are defined globally across all surveys, and the bottom section for parameters which are fit for each survey.}}
	\label{tab:param_summary}
	\begin{tabular}{ll}
		\hline
		Parameter & Description \\
		\hline
		$\Omega_m$  & Matter density  \\
		$w$  &  Dark energy equation of state  \\
		$\alpha$ & Stretch standardisation   \\
		$\beta$         &  Colour standardisation   \\
		$\delta(0)$ & Scale of the mass-magnitude correction\\
		$\delta(\infty)/\delta(0)$ & Redshift-dependence of mass-magnitude correction\\
		$\delta\mathcal{Z}_i$ & Systematics scale\\
		$\delta S$ & Selection effect deviation \\
		$\langle M_B \rangle$ & Mean absolute magnitude \\
		$s_c$ & Colour bias\\
		\hline
		$\langle x_1^i \rangle$ & Mean stretch nodes\\
		$\langle c^i \rangle$ & Mean colour nodes\\
		$\sigma_{M_B}$ & Population magnitude scatter \\
		$\sigma_{x_1}$ & Population stretch scatter \\
		$\sigma_{c}$ & Population colour scatter \\
		$\kappa_{0}$ & Extra colour dispersion\\
		$\kappa_{1}$ & Redshift-dependence of extra colour dispersion\\
		\hline
	\end{tabular}
\end{table}

>>>>

At the most fundamental level, a supernova cosmology analysis is simply a mapping from an underlying population onto an observed population, where cosmology is encoded directly in the mapping function. The difficulty arises both in adequately describing the biases in the mapping function, and in adding sufficient, physically motivated flexibility in both of these populations whilst not adding \textit{too} much flexibility, such that model fitting becomes pathological due to increasing parameter degeneracies within the model. In the following sections, we will describe these layers, mapping functions, and occurrences of these fatal pathologies. Summaries of observables and model parameters are shown in Table \ref{tab:param_summary} for easy reference.

@@

\begin{table}
	\centering
	\caption{{\green Top-level parameters defined in our model and a summary of their use. The parameters are broken into two sections, the top for parameters which are defined globally across all surveys, the second section for parameters which are fit for each survey, the third section are parameters which are defined for each supernova. The bottom section shows the observables (not parameters) that are the input data to the model.}}
	\label{tab:param_summary}
	\begin{tabular}{ll}
		\hline
		Parameter & Description \\
		\hline
		$\Omega_m$  & Matter density  \\
		$w$  &  Dark energy equation of state  \\
		$\alpha$ & Stretch standardisation   \\
		$\beta$         &  Colour standardisation   \\
		$\delta(0)$ & Scale of the mass-magnitude correction\\
		$\delta(\infty)/\delta(0)$ & Redshift-dependence of mass-magnitude correction\\
		$\delta\mathcal{Z}_i$ & Systematics scale\\
		$\delta S$ & Selection effect deviation \\
		$\langle M_B \rangle$ & Mean absolute magnitude \\
		$s_c$ & Colour bias\\
		\hline
		$\langle x_1^i \rangle$ & Mean stretch nodes\\
		$\langle c^i \rangle$ & Mean colour nodes\\
		$\sigma_{M_B}$ & Population magnitude scatter \\
		$\sigma_{x_1}$ & Population stretch scatter \\
		$\sigma_{c}$ & Population colour scatter \\
		$\kappa_{0}$ & Extra colour dispersion\\
		$\kappa_{1}$ & Redshift-dependence of extra colour dispersion\\
		\hline
		$m_B$ & True flux\\
		$x_1$ & True stretch \\
		$c$ & True colour \\
		\hline
		$\hat{m}_B$ & Measured flux\\
		$\hat{x}_1$ & Measured stretch \\
		$\hat{c}$ & Measured colour \\
		$C$ & Covariance on flux, stretch and colour \\
		$\hat{z}$ & Determined redshift \\
		$\hat{m}$ & Determined mass probability \\
		\hline
	\end{tabular}
\end{table}

@@
